---
title: "Testing"
author: "Alexandre Combeau"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#devtools::install_github("vrunge/dust")
library(dust)
#devtools::install_github("jchiquet/aricode")
library(aricode)
#devtools::install_github("gtromano/FOCuS")
library(FOCuS)
library(changepoints)
#devtools::install_github("vrunge/svpChange")
library(svpChange)
```

# Optimal Partitioning using R

```{r OP_R}
n <- 100
gap <- 0.5
chpts <- c(2, 5, 8, 13, 20)*n
data <- dataGenerator_1D(chpts = chpts,
                         parameters = c(0,gap,0,gap,0),
                         sdNoise = 1,
                         type = "gauss")
penalty <- 2 * log(length(data)) * dust::sdDiff(data, "HALL")^2

# OP Algorithm
OP_R <- optimal_partitioning(data, penalty)

# Visualization
par(bg = "white")
plot_segmentation(data, OP_R$changepoints, title = "Optimal Partitioning using R")
cat("Last cost R :", OP_R$costQ[length(OP_R$costQ)], "\n")
cat("OP_R$changepoints :", OP_R$changepoints, "\n")
cat("Expected          :", c(2, 5, 8, 13, 20)*n, "\n")
```

# Optimal Partitioning using Rcpp

```{r OP_Rcpp}
n <- 100
gap <- 1
chpts <- c(2, 5, 8, 13, 20)*n
data <- dataGenerator_1D(chpts = chpts,
                         parameters = c(0,gap,0,gap,0),
                         sdNoise = 1,
                         type = "gauss")
penalty <- 2 * log(length(data)) * dust::sdDiff(data, "HALL")^2

# OP Algorithm
OP_Rcpp <- optimal_partitioning_rcpp(data, penalty)

# Visualization
par(bg = "white")
plot_segmentation(data, OP_Rcpp$changepoints, title = "Optimal Partitioning using Rcpp")
cat("Last cost Rcpp :", OP_Rcpp$costQ[length(OP_Rcpp$costQ)], "\n")
cat("OP_Rcpp$changepoints :", OP_Rcpp$changepoints, "\n")
cat("Expected             :", c(2, 5, 8, 13, 20)*n, "\n")
```

# Time execution between OP (R) and OP (Rcpp)

```{r Exec_Time_OP}
n_vals <- 10^(seq(1, 2, length.out = 40))
gap <- 0.5
temps_R <- numeric(length(n_vals))
temps_Rcpp <- numeric(length(n_vals))
length_data <- integer(length(n_vals))

for (i in 1:length(n_vals))
{
  n <- n_vals[i]
  data <- dataGenerator_1D(chpts = c(2, 5, 8, 13, 20)*n,
                        parameters = c(0,gap,0,gap,0),
                        sdNoise = 1,
                        type = "gauss")
  length_data[i] <- length(data)
  print(length(data))
  penalty <- 2 * log(length(data)) * dust::sdDiff(data, "HALL")^2
  
  # Execution time R
  t0 <- Sys.time()
  optimal_partitioning(data, penalty)
  t1 <- Sys.time()
  temps_R[i] <- as.numeric(difftime(t1, t0, units = "secs"))
  
  # Execution time C++
  t0 <- Sys.time()
  optimal_partitioning_rcpp(data, penalty)
  t1 <- Sys.time()
  temps_Rcpp[i] <- as.numeric(difftime(t1, t0, units = "secs"))
}

lm_R    <- lm(log(temps_R) ~ log(length_data))
lm_Rcpp <- lm(log(temps_Rcpp) ~ log(length_data))

plot(length_data, temps_R, type = "b", pch = 16, col = "red",
     log = "xy",
     xlab = "Length of data",
     ylab = "Time in seconds",
     main = "Execution Time for OP",
     ylim = range(c(temps_R, temps_Rcpp), finite = TRUE),
     xlim = range(length_data, finite = TRUE))
lines(length_data, temps_Rcpp, type = "b", pch = 17, col = "blue")

# Linear prediction for R code
y_pred_R <- exp(coef(lm_R)[1]) * length_data ^ coef(lm_R)[2]
lines(length_data, y_pred_R, col = "black", lty = 2, lwd = 2)

# Linear prediction for Rcpp code
y_pred_Rcpp <- exp(coef(lm_Rcpp)[1]) * length_data ^ coef(lm_Rcpp)[2]
lines(length_data, y_pred_Rcpp, col = "green", lty = 2, lwd = 2)

legend("topleft",
       legend = c(paste("R slope :", round(coef(lm_R)[2], 2)),
                  paste("Rcpp slope :", round(coef(lm_Rcpp)[2], 2))),
       col    = c("red", "blue"),
       pch    = c(16, 17),
       lty    = c(1, 1))
grid()
```

# Pruned Exact Linear Time using R

```{r PELT_R}
n <- 100
gap <- 0.5
data <- dataGenerator_1D(chpts = c(2, 5, 8, 13, 20)*n,
                      parameters = c(0,gap,0,gap,0),
                      sdNoise = 0.2,
                      type = "gauss")
penalty <- 2 * log(length(data))

# PELT Algorithm
PELT_R <- pelt(data, penalty)

# Visualization
plot_segmentation(data, PELT_R$changepoints, title = "PELT using R")
cat("Last cost R :", PELT_R$costQ[length(PELT_R$costQ)], "\n")
cat("PELT_R$changepoints :", PELT_R$changepoints, "\n")
cat("Expected            :", c(2, 5, 8, 13, 20)*n, "\n")
```

# Pruned Exact Linear Time using Rcpp

```{r PELT_Rcpp}
n <- 100
gap <- 0.5
data <- dataGenerator_1D(chpts = c(2, 5, 8, 12, 16, 20)*n,
                      parameters = c(0,gap,0,gap,0,gap),
                      sdNoise = 0.2,
                      type = "gauss")
penalty <- 2 * log(length(data))

# PELT Algorithm
PELT_Rcpp <- pelt_rcpp(data, penalty)

# Visualization
plot_segmentation(data, PELT_Rcpp$changepoints, title = "PELT using Rcpp")
cat("Last cost PELT_Rcpp :", PELT_Rcpp$costQ[length(PELT_Rcpp$costQ)], "\n")
cat("PELT_Rcpp$changepoints :", PELT_Rcpp$changepoints, "\n")
cat("Expected               :", c(2, 5, 8, 12, 16, 20)*n, "\n")
```

# Time execution between PELT (R) and PELT (Rcpp)

```{r Exec_Time_PELT}
n_vals <- 10^(seq(1, 2, length.out = 40))
gap <- 0.5
temps_R <- numeric(length(n_vals))
temps_Rcpp <- numeric(length(n_vals))
length_data <- integer(length(n_vals))

for (i in 1:length(n_vals))
{
  n <- n_vals[i]
  data <- dataGenerator_1D(chpts = c(2, 5, 8, 13, 20)*n,
                        parameters = c(0,gap,0,gap,0),
                        sdNoise = 1,
                        type = "gauss")
  length_data[i] <- length(data)
  print(length(data))
  penalty <- 2 * log(length(data))
  
  # Execution time R
  t0 <- Sys.time()
  pelt(data, penalty)
  t1 <- Sys.time()
  temps_R[i] <- as.numeric(difftime(t1, t0, units = "secs"))
  
  # Execution time C++
  t0 <- Sys.time()
  pelt_rcpp(data, penalty)
  t1 <- Sys.time()
  temps_Rcpp[i] <- as.numeric(difftime(t1, t0, units = "secs"))
}

lm_R    <- lm(log(temps_R) ~ log(length_data))
lm_Rcpp <- lm(log(temps_Rcpp) ~ log(length_data))

plot(length_data, temps_R, type = "b", pch = 16, col = "red",
     log = "xy",
     xlab = "Length of data",
     ylab = "Time in seconds",
     main = "Execution Time for PELT",
     ylim = range(c(temps_R, temps_Rcpp), finite = TRUE),
     xlim = range(length_data, finite = TRUE))
lines(length_data, temps_Rcpp, type = "b", pch = 17, col = "blue")

# Linear prediction for R code
y_pred_R <- exp(coef(lm_R)[1]) * length_data ^ coef(lm_R)[2]
lines(length_data, y_pred_R, col = "black", lty = 2, lwd = 2)

# Linear prediction for Rcpp code
y_pred_Rcpp <- exp(coef(lm_Rcpp)[1]) * length_data ^ coef(lm_Rcpp)[2]
lines(length_data, y_pred_Rcpp, col = "green", lty = 2, lwd = 2)

legend("topleft",
       legend = c(paste("R slope :", round(coef(lm_R)[2], 2)),
                  paste("Rcpp slope :", round(coef(lm_Rcpp)[2], 2))),
       col    = c("red", "blue"),
       pch    = c(16, 17),
       lty    = c(1, 1))
grid()
```

# Smallest Valid Partitioning

```{r SVP_R}
n <- 1000
gap <- 10
chpts = c(0.1,0.3,0.4,0.45,0.55,0.7,0.75,0.95,1)*n
data <- dataGenerator_1D(chpts = chpts,
                         parameters = c(0,gap,0,gap,0,gap,0,gap,0),
                         sdNoise = 1.5)

gamma <- 14
SVP_Range_Rcpp <- smallest_valid_partitioning_rcpp(data,
                                                   gamma,
                                                   test = valid_FOCUS,
                                                   prune_if_unvalid = T,
                                                   prune_if_PELT = F)
plot_segmentation(data, SVP_Range_Rcpp$changepoints,
                  title = paste("SVP_Range_Rcpp, gamma =", round(gamma, 2)))
SVP_Range_Rcpp$nb
cat("SVP_Range_Rcpp$changepoints :", SVP_Range_Rcpp$changepoints, "\n")
cat("Expected                    :", chpts)
```

```{r SVP}
nb_add_data <- 20
temps_R <- numeric(nb_add_data)
length_data <- integer(nb_add_data)
data <- c()
gamma <- 4
for (i in 1:nb_add_data)
{
  data <- c(data, rnorm(50, 1, 1), rnorm(50, 0, 1), rnorm(50, 1, 1), rnorm(50, 0, 1))
  print(i)
  length_data[i] <- 200*i
  
  # Execution time
  t0 <- Sys.time()
  local <- smallest_valid_partitioning_rcpp(data, gamma, valid_FOCUS, T, F)
  t1 <- Sys.time()
  temps_R[i] <- as.numeric(difftime(t1, t0, units = "secs"))
  cat("number of chpts :", length(local$changepoints), "\n")
}

lm_R <- lm(log(temps_R) ~ log(length_data))

plot(length_data, temps_R, type = "b", pch = 16, col = "red",
     log = "xy",
     xlab = "Length of data",
     ylab = "Time in seconds",
     main = "Execution Time : SVP FOCuS",
     ylim = range(temps_R, finite = TRUE),
     xlim = range(length_data, finite = TRUE))

# Linear prediction for R code
y_pred_R <- exp(coef(lm_R)[1]) * length_data ^ coef(lm_R)[2]
lines(length_data, y_pred_R, col = "black", lty = 2, lwd = 2)

legend("topleft",
       legend = c(paste("Slope :", round(coef(lm_R)[2], 2))),
       col    = "red",
       pch    = c(16, 17),
       lty    = c(1, 1))
grid()
```

```{r SVP}
n <- 10^(seq(2, 3, length.out = 8))
temps_R <- numeric(length(n))
gamma <- 8
for (i in 1:length(n))
{
  data <- c(rnorm(n[i]/2, 5, 1), rnorm(n[i]/2, 0, 1))
  print(i)
  
  # Execution time
  t0 <- Sys.time()
  local <- smallest_valid_partitioning(data, gamma, valid_FOCUS)
  t1 <- Sys.time()
  temps_R[i] <- as.numeric(difftime(t1, t0, units = "secs"))
  cat("number of chpts :", length(local$changepoints), "\n")
}

length_data <- n

lm_R <- lm(log(temps_R) ~ log(length_data))

plot(length_data, temps_R, type = "b", pch = 16, col = "red",
     log = "xy",
     xlab = "Length of data",
     ylab = "Time in seconds",
     main = "Execution Time : SVP FOCuS",
     ylim = range(temps_R, finite = TRUE),
     xlim = range(length_data, finite = TRUE))

# Linear prediction for R code
y_pred_R <- exp(coef(lm_R)[1]) * length_data ^ coef(lm_R)[2]
lines(length_data, y_pred_R, col = "black", lty = 2, lwd = 2)

legend("topleft",
       legend = c(paste("Slope :", round(coef(lm_R)[2], 2))),
       col    = "red",
       pch    = c(16, 17),
       lty    = c(1, 1))
grid()
```


```{r SVP_valid_FOCUS}
n <- 300
gap <- 10
data <- dataGenerator_1D(chpts = c(0.1,0.3,0.4,0.45,0.55,0.7,0.75,0.95,1)*n,
                         parameters = c(0,gap,0,gap,0,gap,0,gap,0),
                         sdNoise = 1.5,
                         type = "gauss")
plot(data)
gamma <- 2 * log(length(data)) + 0.5
res1 <- smallest_valid_partitioning_rcpp(data, gamma, valid_FOCUS)
abline(v = res1$changepoints, col = "red")
cat("Obtained :", res1$changepoints, "\n")
cat("Expected :", c(0.1,0.3,0.4,0.45,0.55,0.7,0.75,0.95,1)*n, "\n")
```

# SVP_PELT = PELT ?

```{r SVP_PELT_equal_PELT}
gap <- 2
n <- 500
data <- dataGenerator_1D(chpts = c(0.1,0.3,0.4,0.45,0.55,0.7,0.75,0.95,1)*n,
                         parameters = c(0,gap,0,gap,0,gap,0,gap,0),
                         sdNoise = 1.5)
penalty <- 2 * log(length(data)) * dust::sdDiff(data, method = "HALL")^2
pen <- 30

# Expected
plot(data, type = 'b')
abline(v = c(0.1,0.3,0.4,0.45,0.55,0.7,0.75,0.95,1)*n, col = 2, lwd = 3)

# PELT
resPELT <- pelt_rcpp(data, penalty)
plot_segmentation(data, resPELT$changepoints,
                  title = paste("PELT, penalty =", round(penalty, 2)))

# SVP_OP
SVP_OP <- smallest_valid_partitioning(data, penalty)
cpts <- SVP_OP$changepoints
plot_segmentation(data, SVP_OP$changepoints,
                  title = paste("SVP_valid_OP, gamma =", round(penalty, 2)))

plot(resPELT$nb)
plot(SVP_OP$nb)
res_focus <- smallest_valid_partitioning(data, gamma = pen, test = valid_FOCUS)
plot(res_focus$nb)
resRange <- smallest_valid_partitioning(data, gamma = 8, test = valid_RANGE)
plot(resRange$nb)
resRange_slack <- smallest_valid_partitioning(data, gamma = 4, test = valid_RANGE_SLACK)
plot(resRange_slack$nb)
```

# Comparison of segmentations using ARI

```{r ARI_valid_FOCuS}
n <- 1000
gap <- 2
chpts = c(0.1,0.3,0.4,0.45,0.55,0.7,0.75,0.95,1)*n
data <- dataGenerator_1D(chpts = chpts,
                         parameters = c(0,gap,0,gap,0,gap,0,gap,0),
                         sdNoise = 1.5)
gamma <- 25

res_1 <- smallest_valid_partitioning(data, gamma, test = valid_FOCUS)

res_1$changepoints

plot_segmentation(data, res_1$changepoints,
                  title = paste("valid_FOCuS, gamma =", round(gamma, 2)))

cpts <- c(0, res_1$changepoints)
mean_values <- integer(length(cpts) - 1)
for (i in 1:(length(cpts) - 1))
{
  mean_values[i] <- mean(data[(cpts[i] + 1):cpts[i + 1]])
}

times <- cpts[2]
for (i in 2:length(mean_values))
{
  times[i] <- cpts[i+1] - cpts[i]
}
partition_SVP_FOCUS <- rep(mean_values, times = times)

plot_segmentation(data, chpts, title = "Expected Segmentation")

cpts <- c(0,chpts)
mean_values <- integer(length(cpts) - 1)
for (i in 1:(length(cpts) - 1))
{
  mean_values[i] <- mean(data[(cpts[i] + 1):cpts[i + 1]])
}

times <- cpts[2]
for (i in 2:length(mean_values))
{
  times[i] <- cpts[i+1] - cpts[i]
}
partition_expected <- rep(mean_values, times = times)

ARI(partition_SVP_FOCUS, partition_expected)
```

```{r Exec_Time_PELT}
n_vals <- 10^(seq(1, 1.5, length.out = 3))
gap <- 0.5
temps_R <- numeric(length(n_vals))
temps_Rcpp <- numeric(length(n_vals))
length_data <- integer(length(n_vals))

for (i in 1:length(n_vals))
{
  n <- n_vals[i]
  data <- dataGenerator_1D(chpts = c(2, 5, 8, 13, 20)*n,
                        parameters = c(0,gap,0,gap,0),
                        sdNoise = 1,
                        type = "gauss")
  length_data[i] <- length(data)
  print(length(data))
  gamma <- 10
  
  # Execution time R
  t0 <- Sys.time()
  smallest_valid_partitioning(data, gamma, test = valid_FOCUS)
  t1 <- Sys.time()
  temps_R[i] <- as.numeric(difftime(t1, t0, units = "secs"))
  
  # Execution time C++
  t0 <- Sys.time()
  smallest_valid_partitioning(data, gamma, test = valid_RANGE)
  t1 <- Sys.time()
  temps_Rcpp[i] <- as.numeric(difftime(t1, t0, units = "secs"))
}

lm_R    <- lm(log(temps_R) ~ log(length_data))
lm_Rcpp <- lm(log(temps_Rcpp) ~ log(length_data))

plot(length_data, temps_R, type = "b", pch = 16, col = "red",
     log = "xy",
     xlab = "Length of data",
     ylab = "Time in seconds",
     main = "Execution Time",
     ylim = range(c(temps_R, temps_Rcpp), finite = TRUE),
     xlim = range(length_data, finite = TRUE))
lines(length_data, temps_Rcpp, type = "b", pch = 17, col = "blue")

# Linear prediction for R code
y_pred_R <- exp(coef(lm_R)[1]) * length_data ^ coef(lm_R)[2]
lines(length_data, y_pred_R, col = "black", lty = 2, lwd = 2)

# Linear prediction for Rcpp code
y_pred_Rcpp <- exp(coef(lm_Rcpp)[1]) * length_data ^ coef(lm_Rcpp)[2]
lines(length_data, y_pred_Rcpp, col = "green", lty = 2, lwd = 2)

legend("topleft",
       legend = c(paste("SVP_FOCuS, gamma =", gamma,
                        "; slope =", round(coef(lm_R)[2],2)),
                  paste("SVP_RANGE, gamma =", gamma,
                        "; slope =", round(coef(lm_Rcpp)[2],2))),
       col    = c("red", "blue"),
       pch    = c(16, 17),
       lty    = c(1, 1))
grid()
```

```{r testthat1}
library(testthat)

test_that("SVP with valid_FOCUS and SVP_focus produce similar results", {
  #set.seed(42)
  #n <- 500
  #gap <- 2
  #chpts = c(0.1,0.3,0.4,0.45,0.55,0.7,0.75,0.95,1)*n
  #data <- dataGenerator_1D(chpts = chpts,
  #                       parameters = c(0,gap,0,gap,0,gap,0,gap,0),
  #                       sdNoise = 1.5)
  #gamma <- 15

  # Use valid_FOCUS as the test function
  svp_1 <- smallest_valid_partitioning(data, gamma, test = valid_FOCUS)
  svp_2 <- smallest_valid_partitioning_rcpp(data, gamma, test = valid_FOCUS)
  
  # Their changepoints should be similar
  expect_equal(svp_1$changepoints, svp_2$changepoints, tolerance = 0)

  # Their costQ vectors should be nearly identical
  expect_equal(svp_1$costQ, svp_2$costQ, tolerance = 1e-6)
  
  # Their $nb should be similar
  #expect_equal(svp_1$nb, svp_2$nb, tolerance = 0)
  
  # Their $R should be similar
  expect_equal(svp_1$R, svp_2$R, tolerance = 1e-6)
})
```

```{r Exec_Time_OP}
n_vals <- 10^(seq(1, 3, length.out = 40))
gap <- 0.5
temps_R <- numeric(length(n_vals))
temps_Rcpp <- numeric(length(n_vals))
length_data <- integer(length(n_vals))

for (i in 1:length(n_vals))
{
  n <- n_vals[i]
  data <- dataGenerator_1D(chpts = c(2, 5, 8, 13, 20)*n,
                        parameters = c(0,gap,0,gap,0),
                        sdNoise = 1,
                        type = "gauss")
  length_data[i] <- length(data)
  print(length(data))
  penalty <- 2 * log(length(data)) * dust::sdDiff(data, "HALL")^2
  gamma <- 10
  
  # Execution time R
  t0 <- Sys.time()
  SVP(data, gamma, test = "gaussian_mean")
  t1 <- Sys.time()
  temps_R[i] <- as.numeric(difftime(t1, t0, units = "secs"))
  
  # Execution time C++
  t0 <- Sys.time()
  pelt_rcpp(data, penalty)
  t1 <- Sys.time()
  temps_Rcpp[i] <- as.numeric(difftime(t1, t0, units = "secs"))
}

lm_R    <- lm(log(temps_R) ~ log(length_data))
lm_Rcpp <- lm(log(temps_Rcpp) ~ log(length_data))

plot(length_data, temps_R, type = "b", pch = 16, col = "red",
     log = "xy",
     xlab = "Length of data",
     ylab = "Time in seconds",
     main = "Execution Time SVP / OP",
     ylim = range(c(temps_R, temps_Rcpp), finite = TRUE),
     xlim = range(length_data, finite = TRUE))
lines(length_data, temps_Rcpp, type = "b", pch = 17, col = "blue")

# Linear prediction for R code
y_pred_R <- exp(coef(lm_R)[1]) * length_data ^ coef(lm_R)[2]
lines(length_data, y_pred_R, col = "black", lty = 2, lwd = 2)

# Linear prediction for Rcpp code
y_pred_Rcpp <- exp(coef(lm_Rcpp)[1]) * length_data ^ coef(lm_Rcpp)[2]
lines(length_data, y_pred_Rcpp, col = "green", lty = 2, lwd = 2)

legend("topleft",
       legend = c(paste("SVP slope :", round(coef(lm_R)[2], 2)),
                  paste("PELT slope :", round(coef(lm_Rcpp)[2], 2))),
       col    = c("red", "blue"),
       pch    = c(16, 17),
       lty    = c(1, 1))
grid()
```

==> Rcpp::compileAttributes()

* Updated R/RcppExports.R

==> devtools::document(roclets = c('rd', 'collate', 'namespace'))

ℹ Updating changepoints documentation
ℹ Loading changepoints
✖ Skipping NAMESPACE
ℹ It already exists and was not generated by roxygen2.
Documentation completed

==> R CMD INSTALL --preclean --no-multiarch --with-keep.source changepoints-main

* installing to library ‘/opt/homebrew/lib/R/4.5/site-library/_build’
* installing *source* package ‘changepoints’ ...
** this is package ‘changepoints’ version ‘1.0’
** using staged installation
** libs
clang++ -std=gnu++17 -I"/opt/homebrew/Cellar/r/4.5.1/lib/R/include" -DNDEBUG  -I'/opt/homebrew/lib/R/4.5/site-library/Rcpp/include' -I/opt/homebrew/opt/gettext/include -I/opt/homebrew/opt/readline/include -I/opt/homebrew/opt/xz/include -I/opt/homebrew/include    -fPIC  -g -O2   -c RcppExports.cpp -o RcppExports.o
using C++ compiler: ‘Apple clang version 17.0.0 (clang-1700.0.13.5)’
using SDK: ‘MacOSX15.5.sdk’
clang++ -std=gnu++17 -I"/opt/homebrew/Cellar/r/4.5.1/lib/R/include" -DNDEBUG  -I'/opt/homebrew/lib/R/4.5/site-library/Rcpp/include' -I/opt/homebrew/opt/gettext/include -I/opt/homebrew/opt/readline/include -I/opt/homebrew/opt/xz/include -I/opt/homebrew/include    -fPIC  -g -O2   -c SVP.cpp -o SVP.o
In file included from SVP.cpp:1:
In file included from ./tests.h:2:
In file included from ./focus.h:17:
In file included from /Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/iostream:42:
In file included from /Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/ios:220:
In file included from /Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__locale:15:
In file included from /Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__memory/shared_ptr.h:32:
/Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__memory/unique_ptr.h:81:5: warning: delete called on 'Piece' that is abstract but has non-virtual destructor [-Wdelete-abstract-non-virtual-dtor]
   81 |     delete __ptr;
      |     ^
/Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__memory/unique_ptr.h:293:7: note: in instantiation of member function 'std::default_delete<Piece>::operator()' requested here
  293 |       __ptr_.second()(__tmp);
      |       ^
/Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__memory/unique_ptr.h:262:71: note: in instantiation of member function 'std::unique_ptr<Piece>::reset' requested here
  262 |   _LIBCPP_HIDE_FROM_ABI _LIBCPP_CONSTEXPR_SINCE_CXX23 ~unique_ptr() { reset(); }
      |                                                                       ^
./focus.h:169:35: note: in instantiation of member function 'std::unique_ptr<Piece>::~unique_ptr' requested here
  169 |       initpsl.push_back(std::move(newP(0.0, 0, 0.0)));
      |                                   ^
clang++ -std=gnu++17 -I"/opt/homebrew/Cellar/r/4.5.1/lib/R/include" -DNDEBUG  -I'/opt/homebrew/lib/R/4.5/site-library/Rcpp/include' -I/opt/homebrew/opt/gettext/include -I/opt/homebrew/opt/readline/include -I/opt/homebrew/opt/xz/include -I/opt/homebrew/include    -fPIC  -g -O2   -c SVP0.cpp -o SVP0.o
1 warning generated.
clang++ -std=gnu++17 -I"/opt/homebrew/Cellar/r/4.5.1/lib/R/include" -DNDEBUG  -I'/opt/homebrew/lib/R/4.5/site-library/Rcpp/include' -I/opt/homebrew/opt/gettext/include -I/opt/homebrew/opt/readline/include -I/opt/homebrew/opt/xz/include -I/opt/homebrew/include    -fPIC  -g -O2   -c focus.cpp -o focus.o
In file included from focus.cpp:14:
In file included from ./focus.h:17:
In file included from /Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/iostream:42:
In file included from /Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/ios:220:
In file included from /Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__locale:15:
In file included from /Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__memory/shared_ptr.h:32:
/Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__memory/unique_ptr.h:81:5: warning: delete called on 'Piece' that is abstract but has non-virtual destructor [-Wdelete-abstract-non-virtual-dtor]
   81 |     delete __ptr;
      |     ^
/Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__memory/unique_ptr.h:293:7: note: in instantiation of member function 'std::default_delete<Piece>::operator()' requested here
  293 |       __ptr_.second()(__tmp);
      |       ^
/Library/Developer/CommandLineTools/SDKs/MacOSX.sdk/usr/include/c++/v1/__memory/unique_ptr.h:262:71: note: in instantiation of member function 'std::unique_ptr<Piece>::reset' requested here
  262 |   _LIBCPP_HIDE_FROM_ABI _LIBCPP_CONSTEXPR_SINCE_CXX23 ~unique_ptr() { reset(); }
      |                                                                       ^
./focus.h:169:35: note: in instantiation of member function 'std::unique_ptr<Piece>::~unique_ptr' requested here
  169 |       initpsl.push_back(std::move(newP(0.0, 0, 0.0)));
      |                                   ^
clang++ -std=gnu++17 -I"/opt/homebrew/Cellar/r/4.5.1/lib/R/include" -DNDEBUG  -I'/opt/homebrew/lib/R/4.5/site-library/Rcpp/include' -I/opt/homebrew/opt/gettext/include -I/opt/homebrew/opt/readline/include -I/opt/homebrew/opt/xz/include -I/opt/homebrew/include    -fPIC  -g -O2   -c optimal_partitioning_rcpp.cpp -o optimal_partitioning_rcpp.o
1 warning generated.
clang++ -std=gnu++17 -I"/opt/homebrew/Cellar/r/4.5.1/lib/R/include" -DNDEBUG  -I'/opt/homebrew/lib/R/4.5/site-library/Rcpp/include' -I/opt/homebrew/opt/gettext/include -I/opt/homebrew/opt/readline/include -I/opt/homebrew/opt/xz/include -I/opt/homebrew/include    -fPIC  -g -O2   -c pelt_rcpp.cpp -o pelt_rcpp.o
clang++ -std=gnu++17 -dynamiclib -Wl,-headerpad_max_install_names -undefined dynamic_lookup -L/opt/homebrew/Cellar/r/4.5.1/lib/R/lib -L/opt/homebrew/opt/gettext/lib -L/opt/homebrew/opt/readline/lib -L/opt/homebrew/opt/xz/lib -L/opt/homebrew/lib -o changepoints.so RcppExports.o SVP.o SVP0.o focus.o optimal_partitioning_rcpp.o pelt_rcpp.o -L/opt/homebrew/Cellar/r/4.5.1/lib/R/lib -lR
installing to /opt/homebrew/lib/R/4.5/site-library/_build/00LOCK-changepoints-main/00new/changepoints/libs
** R
** byte-compile and prepare package for lazy loading
** help
*** installing help indices
** building package indices
** testing if installed package can be loaded from temporary location
** checking absolute paths in shared objects and dynamic libraries
** testing if installed package can be loaded from final location
** testing if installed package keeps a record of temporary installation path
* DONE (changepoints)
library(FOCuS)





